Analysis

### 2022-06-17 production/prod_analysis-fix-t5.Rmd
ajustes labels descriptives

```{r tab-desc, results="asis", warning=FALSE}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools
               )
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))
# Css
st_css()
st_options(lang = "en",
           footnote = NA,
           bootstrap.css = F,
           custom.css = here::here("input/css/dfsummary.css"),
           dfSummary.custom.1 = NA
           )

# Df variables nivel 1 __________________________________________________________
df_study1 <- 
  df_study_long_t5_comunas %>% 
  select(in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         conviviality, identity,
         in_amreal,educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) 
lab_study1 <- sjlabelled::get_label(df_study1) 
df_study1 <- df_study1 %>% na.omit() %>% sjlabelled::set_label(lab_study1)

>>>>

```{r tab-desc, results="asis", warning=FALSE}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               sjlabelled
               )
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))
# Css
st_css()
st_options(lang = "en",
           footnote = NA,
           bootstrap.css = F,
           custom.css = here::here("input/css/dfsummary.css"),
           dfSummary.custom.1 = NA
           )

# Df variables nivel 1 __________________________________________________________
df_study1 <- 
  df_study_long_t5_comunas %>% 
  select(in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         conviviality, identity,
         in_amreal,
         educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm)

lab_study1 <- sjlabelled::get_label(df_study1)

df_study1$in_ansied <- factor(df_study1$in_ansied,1:5,get_labels(df_study1$in_ansied))
df_study1$in_simpat <- factor(df_study1$in_simpat,1:5,get_labels(df_study1$in_simpat))
df_study1$in_valfam <- factor(df_study1$in_valfam,1:5,get_labels(df_study1$in_valfam))
df_study1$in_valami <- factor(df_study1$in_valami,1:5,get_labels(df_study1$in_valami))
df_study1$in_amigcl <- factor(df_study1$in_amigcl,1:5,get_labels(df_study1$in_amigcl))

df_study1$in_simili <- factor(df_study1$in_simili,1:5,get_labels(df_study1$in_simili))
df_study1$in_amsimb <- factor(df_study1$in_amsimb,1:5,get_labels(df_study1$in_amsimb))
df_study1$in_acpier <- factor(df_study1$in_acpier,1:5,get_labels(df_study1$in_acpier))
df_study1$in_acadop <- factor(df_study1$in_acadop,1:5,get_labels(df_study1$in_acadop))

df_study1$in_amreal <- factor(df_study1$in_amreal,1:5,get_labels(df_study1$in_amreal))

df_study1 <- df_study1 %>% na.omit() %>% sjlabelled::set_label(lab_study1)
